Democracy, Public Support, and Measurement Uncertainty

### 2021-06-06 paper/dcpo_demsupport.Rmd
changed theta to theta_trim for apsr models. The results should yield the same x_scale with MOC now. @sammo3182

claassen_replication <- readRDS(here("data", "claassen_replication.rds")) %>% 
  janitor::clean_names() %>% 
  DCPOtools::with_min_yrs(2)
load(here("data", "claassen_m5_theta.rda"))
load(here("data", "dem_mood_apsr.RData"))
load(here("data", "dcpo_input.rda"))
load(here("data", "dcpo_theta.rda"))
load(here("data", "dcpo_sigma.rda"))
load(here("data", "dcpo_ajps_rubin.rda"))
df_dcpoUncertainAPSR <- readRDS(here("data", "df_dcpoUncertainAPSR.rds"))

@@

ls_eqECM <- glue("diff(theta, lag = 1) ~ plm::lag(theta, 1:2) + {ls_ivECM} + diff(lnGDP_imp, lag = 1) + plm::lag(lnGDP_imp, 1)") %>% 
  outer(ls_ctrlECM, paste0) %>% 
  as.vector()

@@

ls_eqFD <- glue("diff(theta, lag = 1) ~ {ls_ivFD} + lnGDP_imp") %>% 
  outer(ls_ctrlFD, paste0) %>% 
  as.vector()

ls_mod_apsrCLS <- c(
  glue("plm({ls_eqECM}, model = 'pooling', data = aData)"),
  glue("plm({ls_eqFD}, model = 'fd', index = 'Country', data = aData)")
)
```

@@

ls_eqECM <- glue("diff(theta, lag = 1) ~ plm::lag(theta, 1:2) + {ls_ivECM} + diff(lg_imp_mdpgdp, lag = 1) + plm::lag(lg_imp_mdpgdp, 1)") %>% 
  outer(ls_ctrlECM, paste0) %>% 
  as.vector()

@@

ls_eqFD <- glue("theta ~ {ls_ivFD} + lg_imp_mdpgdp") %>% 
  outer(ls_ctrlFD, paste0) %>% 
  as.vector()

@@

```{r dcpo-uncertainAJPSmain, eval=FALSE}
df_dcpo <- dcpo_ajps_rubin %>% map2(1:length(dcpo_ajps_rubin), ~ {
  .x[[.y]] %>%
    mutate(theta_dem = theta * regime,
           theta_aut = theta * (1 - regime)) %>%
    plm::pdata.frame(index = c("country", "year"))
}) # The code is to fit the embedded format of dcpo_ajps_rubin

>>>>

claassen_replication <- readRDS(here("data", "claassen_replication.rds")) %>% 
  janitor::clean_names() %>% 
  DCPOtools::with_min_yrs(2)
load(here("data", "claassen_m5_theta.rda"))
load(here("data", "dem_mood_apsr.RData"))
load(here("data", "dcpo_input.rda"))
load(here("data", "dcpo_theta.rda"))
load(here("data", "dcpo_sigma.rda"))
#load(here("data", "dcpo_ajps_rubin.rda"))
# df_controls <- readRDS(here("data", "control_variables_ajps.rds"))   #use control file for merging with 
df_dcpoUncertainAPSR <- readRDS(here("data", "df_dcpoUncertainAPSR.rds"))

@@

@@

ls_eqFD <- glue("diff(SupDem_trim, lag = 1) ~ {ls_ivFD} + lnGDP_imp") %>% 
  outer(ls_ctrlFD, paste0) %>% 
  as.vector()

ls_mod_apsrCLS <- c(
  glue("plm({ls_eqECM}, model = 'pooling', data = aData)"),
  glue("plm({ls_eqFD}, model = 'fd', index = 'country', data = aData)")
)
```

@@

ls_eqECM <- glue("diff(theta_trim, lag = 1) ~ plm::lag(theta_trim, 1:2) + {ls_ivECM} + diff(lg_imp_mdpgdp, lag = 1) + plm::lag(lg_imp_mdpgdp, 1)") %>% 
  outer(ls_ctrlECM, paste0) %>% 
  as.vector()

@@

ls_eqFD <- glue("theta_trim ~ {ls_ivFD} + lg_imp_mdpgdp") %>% 
  outer(ls_ctrlFD, paste0) %>% 
  as.vector()

@@

```{r dcpo-uncertainAJPSmain, eval=FALSE}
# df_dcpo <- dcpo_ajps_rubin %>% map2(1:length(dcpo_ajps_rubin), ~ {
#  .x[[.y]] %>%
#    mutate(theta_dem = theta * regime,
#           theta_aut = theta * (1 - regime)) %>%
#    plm::pdata.frame(index = c("country", "year"))
# }) # The code is to fit the embedded format of dcpo_ajps_rubin
